Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-25 PAPER.tex
updated fig B3 to match
re-made fig 20 with sigloss updates

Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to not weighting (blue dashed line). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is small.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. full inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text. Overall the limits show good agreement, with k modes differing by factors of $\sim$$3$.

>>>>

Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
is beneficial compared to not weighting (blue dashed line). In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes. We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
only the strongest $\sim3$-$4$ eigenmodes are down-weighted. %, though the improvement from the unweighted case is small.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. full inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text. Overall the limits show good agreement, with k modes differing by factors of $\sim$$2$ for $k > 0.1$ $h$Mpc$^{-1}$ .
